Analysis

### 2020-01-16 script/analysis.Rmd
update-desc

@@

grafyear3

@@

```{r}
reg_year<- lm(lngap_just~lngap_perc*as.factor(year), data=clw3 )

@@

```{r}
load("input/data/processed/clw3.Rdata")
names(clw3)

datw3 <- clw3[,c("lngap_perc","lngap_just","educ_rec","Quint")]

datw3$educ_rec    <- factor(datw3$educ_rec,levels = c(1,2,3,4),labels =c("Ed.Básica","Ed.Media", "Ed.Sup.Incomp.", "Ed.Universitaria"))
datw3$Quint       <- factor(datw3$Quint,levels = c(1,2,3,4,5),labels = c("Quintil 1","Quintil 2","Quintil 3","Quintil 4","Quintil 5"))

datw3

tab01<- psych::describe(datw3[,c("lngap_perc","lngap_just")],fast=TRUE)
tab01a<-select(tab01,n,mean,sd,min,max)
tab01a<- round(tab01a,digits = 2)
tab01a <- as.data.frame(tab01a)

tab01a$mean <- paste0(tab01a$mean," (",tab01a$sd,")")
tab01a$sd <- NULL
names(tab01a) <- c("n","m_sd_pct","min","max")

tab01a

tab02<- rbind(
questionr::freq(na.omit(datw3$educ_rec),valid = F),
questionr::freq(na.omit(datw3$Quint),valid = F))
#questionr::freq(na.omit(datw3$redis_dummy),valid = F))
tab02$min <- NA
tab02$max <- NA
names(tab02) <- c("n","m_sd_pct","min","max")

tab03<- rbind(tab01a,tab02)
options(knitr.kable.NA = '')

tab03$var <- rownames(tab03)
tab03$var[tab03$var=="lngap_perc"] <- "Percibida"
tab03$var[tab03$var=="lngap_just"] <- "Justa"

tab03$mod <- c("Brecha Salarial","Brecha Salarial","Educación","Educación","Educación","Educación",
               "Ingreso","Ingreso","Ingreso","Ingreso","Ingreso")

tab03 <- select(tab03,mod,var,everything())

sink("output/tables/desc.html")
kableExtra::kable(tab03,format = "html",booktabs=T ,row.names = F,col.names = c("Dimensión","N","Variable/niveles","Media(DS)","Min","Max")) %>%
  kable_styling() %>%
    collapse_rows(columns = 1,valign = "middle")
sink()
```

>>>>

-VENDEN BIEN LAPOMA.

@@

@@

```{r}
reg_year<- lm(lngap_just~lngap_perc*year, data=clw3 )

@@

```{r}
load("input/data/processed/clw3.RData")
load("input/data/processed/dat99.RData")
load("input/data/processed/dat09.RData")
load("input/data/processed/dat19.RData")
names(clw3)

datw3 <- clw3[,c("lngap_perc","lngap_just","educ_rec","Quint","redis_dummy","year")]

datw3$educ_rec    <- factor(datw3$educ_rec,levels = c(1,2,3,4),
                            labels =c("Ed.Básica",
                                      "Ed.Media",
                                      "Ed.Sup.Incomp.",
                                      "Ed.Universitaria"))
datw3$Quint       <- factor(datw3$Quint,levels = c(1,2,3,4,5),
                            labels = c("Quintil 1",
                                       "Quintil 2",
                                       "Quintil 3",
                                       "Quintil 4",
                                       "Quintil 5"))

dat01<- subset(x = datw3,year==1999)
dat02<- subset(x = datw3,year==2009)
dat03<- subset(x = datw3,year==2019)

dat01$income_pc <- dat99$ingreso_pc
dat02$income_pc <- dat09$ingreso_pc
dat03$income_pc <- dat19$ingreso_pc

# Media (DS) ----------------------------------#

tab01<- psych::describe(dat01[,c("lngap_perc","lngap_just")],fast=TRUE)
tab01a<-select(tab01,n,mean,sd,min,max)
tab01a<- round(tab01a,digits = 2)
tab01a <- as.data.frame(tab01a)
tab01a$var<- rownames(tab01a)

tab01a <- tab01a %>% select(var,everything())

tab01a$mean <- paste0(tab01a$mean," (",tab01a$sd,")")
tab01a$sd <- NULL
names(tab01a) <- c("var","n","m_sd_pct","min","max")

tab02<- psych::describe(dat02[,c("lngap_perc","lngap_just")],fast=TRUE)
tab02a<-select(tab02,n,mean,sd,min,max)
tab02a<- round(tab02a,digits = 2)
tab02a <- as.data.frame(tab02a)
tab02a$var<- rownames(tab02a) 
tab02a <- tab02a %>% select(var,everything())
tab02a$mean <- paste0(tab02a$mean," (",tab02a$sd,")")
tab02a$sd <- NULL
names(tab02a) <- c("var","n","m_sd_pct","min","max")

tab03<- psych::describe(dat03[,c("lngap_perc","lngap_just")],fast=TRUE)
tab03a<-select(tab03,n,mean,sd,min,max)
tab03a<- round(tab03a,digits = 2)
tab03a <- as.data.frame(tab03a)
tab03a$var<- rownames(tab03a)

tab03a <- tab03a %>% select(var,everything())

tab03a$mean <- paste0(tab03a$mean," (",tab03a$sd,")")
tab03a$sd <- NULL
names(tab03a) <- c("var","n","m_sd_pct","min","max")

# Frecuencias----------------------------------#

freq01<- rbind(
na.omit(dat01) %>% group_by(educ_rec) %>% summarise(n=n()) %>% mutate(m_sd_pct=n/sum(n)*100,min=NA,max=NA) %>% rename(var=educ_rec),
dat01 %>% select(Quint,income_pc) %>% group_by(Quint) %>% summarise(n=n(),m_sd_pct=mean(income_pc),min=min(income_pc),max=max(income_pc)) %>% rename(var=Quint) %>% na.omit())
names(freq01) <- c("var","n","m_sd_pct","min","max")
freq01$m_sd_pct <- round(freq01$m_sd_pct,2)
freq01$min      <- round(freq01$min,2)
freq01$max      <- round(freq01$max,2)
table01<- rbind(tab01a,freq01)
table01$var[table01$var=="lngap_perc"] <- "Percibida"
table01$var[table01$var=="lngap_just"] <- "Justa"

table01$mod <- c("Brecha Salarial",
                 "Brecha Salarial",
                 "Educación",
                 "Educación",
                 "Educación",
                 "Educación",
                 "Ingreso",
                 "Ingreso",
                 "Ingreso",
                 "Ingreso",
                 "Ingreso")
table01$year <- 1999
table01 <- table01 %>% select(year,mod,everything())
#------------------------------------------------------2009#
freq02<- rbind(
na.omit(dat02) %>% group_by(educ_rec) %>% summarise(n=n()) %>% mutate(m_sd_pct=n/sum(n)*100,min=NA,max=NA) %>% rename(var=educ_rec),
dat02 %>% select(Quint,income_pc) %>% group_by(Quint) %>% summarise(n=n(),m_sd_pct=mean(income_pc),min=min(income_pc),max=max(income_pc)) %>% rename(var=Quint) %>% na.omit())
names(freq02) <- c("var","n","m_sd_pct","min","max")
freq02$m_sd_pct <- round(freq02$m_sd_pct,2)
freq02$min      <- round(freq02$min,2)
freq02$max      <- round(freq02$max,2)
table02<- rbind(tab02a,freq02)

table02$var[table02$var=="lngap_perc"] <- "Percibida"
table02$var[table02$var=="lngap_just"] <- "Justa"

table02$mod <- c("Brecha Salarial",
                 "Brecha Salarial",
                 "Educación",
                 "Educación",
                 "Educación",
                 "Educación",
                 "Ingreso",
                 "Ingreso",
                 "Ingreso",
                 "Ingreso",
                 "Ingreso")
table02$year <- 2009
table02 <- table02 %>% select(year,mod,everything())

#------------------------------------------------------2019#
freq03<- rbind(
na.omit(dat03) %>% group_by(educ_rec) %>% summarise(n=n()) %>% mutate(m_sd_pct=n/sum(n)*100,min=NA,max=NA) %>% rename(var=educ_rec),
dat03 %>% select(Quint,income_pc) %>% group_by(Quint) %>% summarise(n=n(),m_sd_pct=mean(income_pc),min=min(income_pc),max=max(income_pc)) %>% rename(var=Quint) %>% na.omit())
names(freq03) <- c("var","n","m_sd_pct","min","max")
freq03$m_sd_pct <- round(freq03$m_sd_pct,2)
freq03$min      <- round(freq03$min,2)
freq03$max      <- round(freq03$max,2)

table03<- rbind(tab02a,freq03)

table03$var[table03$var=="lngap_perc"] <- "Percibida"
table03$var[table03$var=="lngap_just"] <- "Justa"

table03$mod <- c("Brecha Salarial",
                 "Brecha Salarial",
                 "Educación",
                 "Educación",
                 "Educación",
                 "Educación",
                 "Ingreso",
                 "Ingreso",
                 "Ingreso",
                 "Ingreso",
                 "Ingreso")
table03$year <- 2019
table03 <- table03 %>% select(year,mod,everything())

desc01 <- rbind(table01,table02,table03)

```{r}
options(knitr.kable.NA = '')
kable(desc01,format = "html",
      align = c("l"),
      booktabs=T,
      row.names = F,
      col.names = c("Año","Dimensión","N","Variable/nivel","Media(DS)/%","Min","Max")) %>% 
  kable_styling(full_width = F) %>% 
  collapse_rows(columns = 1:2,valign = "middle",row_group_label_position = 'stack') %>% 
  cat(., file = "output/tables/desc.html")
```
